# Intro to Probability

## Exercise 3.1

```{r message=FALSE}
library(tidyverse)

set.seed(123)

# Number of coin flips
N <- 500
p <- 0.8

flips <- sample(x=c("H", "T"), prob=c(p, 1-p), size=N, replace=TRUE)
Phead <- cumsum(flips=="H") / (1:N)

ggplot() +
  geom_line(mapping=aes(x=1:N, y=Phead), alpha=0.5) +
  geom_hline(mapping=aes(yintercept=p), color="red")
```

## Exercise 3.2

A. $P[X=10] = \frac{8}{48} = \frac{1}{6}$

B. $P[X=10 or X=Jack] = \frac{1}{6} + \frac{1}{6} = \frac{1}{3}$

## Exercise 3.3

A.

```{r results="hold"}
dx <- 0.01
x <- seq(0, 1, dx)
px <- 6*x * (1-x)

ggplot()+
  geom_line(mapping=aes(x=x, y=px)) +
  labs(title="pdf")

# Approximate Integral
area = sum(dx * px)
paste("The area under the curve is approximately", area)

```


B. 
\begin{align*}
  \int_0^1 6x(1-x) dx &= \int_0^1 6xdx - \int_0^1 6x^2dx \\
                      &= 3x^2 \rvert_0^1 - 2x^3 \rvert_0^1 \\
                      &= 3 - 2 \\
                      &= 1
\end{align*}

C. Yes, it satisfies equation 3.3.

D. The maximum value of $p(x) = `r max(px)`

## Exercsie 3.4

A. and B.
```{r results="hold"}
mu <- 162
sigma <- 15

dx <- 0.01
x <- seq(mu-sigma, mu+sigma, dx)
px <- 1/(sigma * sqrt(2*pi)) * exp(-((x-mu)/sigma)^2/2)

ggplot()+
  geom_line(mapping=aes(x=x, y=px)) +
  labs(title="pdf")

# Approximate Integral
area = sum(dx * px)
paste("The area under the curve is approximately", round(area, 2))

```

## Exercise 3.5

$P[grade=1st] = 0.2, P[grade=6th]=0.2, P[grade=11th]=0.6$

Conjoint Table

| Grade | Ice Cream | Fruit | French Fries |
| ----- | --------- | ----- | ------------ |
| 1st   |   0.06    | 0.12  |    0.02      |
| 6th   |   0.12    | 0.06  |    0.02      |
| 11th  |   0.18    | 0.06  |    0.36      |

Grade and favorite food are independent if $P[\text{favorite food | grade}] = P[\text{favorite food}]$

$$P[\text{ice cream} | 1st] = 0.3 \ne P[\text{ice cream}] = 0.36$$
$\therefore$ Grade and favorite food are not independent.


